---
title: "ggplot2 Book Data Viz thru Chapter 3"
author: "Casey Bates"
date: "11/3/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Import cleaned dataset.
```{r, message=FALSE}
library(tidyverse)
garfield_df <- read_csv("garfield_no_zeros_clean.csv")
```
Basic bar chart of sales by location:
```{r}
ggplot(garfield_df, aes(Location)) + 
  geom_bar()
```

```{r}
ggplot(garfield_df, aes(Location, fill = Classification,)) + 
  geom_bar()
```
For a continuous variable, you also need to group by that variable
```{r}
ggplot(garfield_df, aes(Location, fill = Sale_Price, group = Sale_Price)) + 
  geom_bar()
```


Histogram of sales by sale price:
```{r}
ggplot(garfield_df, aes(Sale_Price)) +
  geom_histogram(binwidth = 10000)
```

```{r}
ggplot(garfield_df, aes(Sale_Price)) +
  geom_freqpoly(binwidth = 10000)
```

```{r}
ggplot(garfield_df, aes(Sale_Price, color = Location)) +
  geom_freqpoly(binwidth = 10000)
```


```{r}
ggplot(garfield_df, aes(Sale_Price)) +
  geom_histogram(binwidth = 25000)
```
Square footage
```{r}
ggplot(garfield_df, aes(Square_Feet)) +
  geom_histogram(binwidth = 100)
```

```{r}
ggplot(garfield_df, aes(Square_Feet)) +
  geom_freqpoly(binwidth = 100)
```


```{r}
ggplot(garfield_df, aes(Square_Feet)) +
  geom_histogram(binwidth = 50)
```

```{r}
ggplot(garfield_df, aes(Square_Feet)) +
  geom_freqpoly(binwidth = 50)
```

```{r}
ggplot(garfield_df, aes(Sale_Date)) +
  geom_histogram(bins = 104) # Number of weeks of data in the dataset
```

```{r}
ggplot(garfield_df, aes(Sale_Date)) +
  geom_freqpoly(bins = 104) # Number of weeks of data in the dataset
```

Scatterplot
```{r}
ggplot(garfield_df, aes(Square_Feet, Sale_Price, color = Location)) +
  geom_point(alpha = 0.5)
```

```{r}
ggplot(garfield_df, aes(Square_Feet, Sale_Price)) +
  geom_point(alpha = 0.5) +
  geom_smooth()
```


```{r}
ggplot(garfield_df, aes(Square_Feet, Sale_Price, color = Location)) +
  geom_point(alpha = 0.5) +
  geom_smooth()
```

```{r}
ggplot(garfield_df, aes(Square_Feet, Sale_Price, color = Location)) +
  geom_point(alpha = 0.5) +
  geom_smooth(span = 0.5)
```


```{r}
ggplot(garfield_df, aes(Square_Feet, Sale_Price, color = Location)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm")
```

```{r}
ggplot(garfield_df, aes(Square_Feet, Sale_Price, color = Location)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm") +
  facet_wrap(~ Location)
```

```{r}
ggplot(garfield_df, aes(Square_Feet, Sale_Price, color = Location)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm") +
  facet_wrap(~ Classification)
```

```{r}
ggplot(garfield_df, aes(Location, Sale_Price, color=Classification)) +
  geom_jitter(alpha = 0.5)
```

```{r}
ggplot(garfield_df, aes(Location, Sale_Price)) +
  geom_boxplot()
```

```{r}
ggplot(garfield_df, aes(Location, Sale_Price)) +
  geom_point() +
  geom_boxplot()
```
Re-order boxplots by median sale price
```{r}
ggplot(garfield_df, aes(x = reorder(Location, Sale_Price, fun = median), y = Sale_Price, fill = Location)) +
  geom_boxplot()
```


```{r}
ggplot(garfield_df, aes(Location, Sale_Price)) +
  geom_violin()
```

```{r}
ggplot(garfield_df, aes(Architectural_Style)) + 
  geom_bar()
```

```{r}
qplot(Sale_Date, data = garfield_df)
```

```{r}
qplot(Sale_Date, Sale_Price, data = garfield_df)
```

```{r}
qplot(Square_Feet, Sale_Price, data = garfield_df)
```

```{r}
ggplot(garfield_df, aes(Square_Feet, Sale_Price, fill = Location, color = Location)) +
  geom_polygon(alpha = 0.3)
```

```{r}
ggplot(garfield_df, aes(Square_Feet, Sale_Price)) +
  geom_area()
```

```{r}
ggplot(garfield_df, aes(Square_Feet, Sale_Price)) +
  geom_text(aes(label = Location), check_overlap = TRUE)
```

```{r}
ggplot(garfield_df, aes(Square_Feet, Sale_Price, color = Location)) +
  geom_point(show.legend = FALSE) + 
  directlabels::geom_dl(aes(label = Location), method = "smart.grid")
```
A little surprised by the placement of the New Castle label.

```{r}
ggplot(garfield_df, aes(Year_Built, color = Location)) +
  geom_freqpoly()
```

```{r}
ggplot(garfield_df, aes(Year_Built, color = Location)) +
  geom_freqpoly(binwidth = 2)
```

```{r}
ggplot(garfield_df, aes(Year_Built, color = Location)) +
  geom_freqpoly(binwidth = 10)
```

#3.13 Statistical Summaries
```{r}
ggplot(garfield_df, aes(Location, Year_Built)) +
  geom_bar(stat = "summary_bin", fun.y = mean)
```
Really, do all sales have the same mean Year Built?! I'll check this formula on another variable to make sure it's working...
```{r}
ggplot(garfield_df, aes(Location, Sale_Price)) +
  geom_bar(stat = "summary_bin", fun.y = mean)
```
It looks like it's working. Strange.
```{r}
ggplot(garfield_df, aes(Location, Square_Feet)) +
  geom_bar(stat = "summary_bin", fun.y = mean)
```
Max sale price...
```{r}
ggplot(garfield_df, aes(Location, Sale_Price)) +
  geom_bar(stat = "summary_bin", fun.y = max)
```
Standard deviation...
```{r}
ggplot(garfield_df, aes(Location, Sale_Price)) +
  geom_bar(stat = "summary_bin", fun.y = sd)
```
2d summary plot attempt
```{r}
ggplot(garfield_df, aes(Square_Feet, Year_Built, z = Sale_Price)) +
  geom_raster(binwidth = 10, stat = "summary_2d", fun = mean, na.rm = TRUE)
```
What if we divide square feet by 10 to get bins of the same size
```{r}
ggplot(garfield_df, aes(Square_Feet/10, Year_Built, z = Sale_Price)) +
  geom_raster(binwidth = 10, stat = "summary_2d", fun = mean, na.rm = TRUE)
```
Maybe try something less spread out along the x axis
```{r}
ggplot(garfield_df, aes(Bedrooms, Baths, z = Sale_Price)) +
  geom_raster(binwidth = 0.25, stat = "summary_2d", fun = mean, na.rm = TRUE) #Baths listed in 0.25 increments
```
Documentation says that geom_raster is a "high performance special case for when all the tiles are the same size". Here's the above with a binwidth = 1 (to match bedrooms)
```{r}
ggplot(garfield_df, aes(Bedrooms, Baths, z = Sale_Price)) +
  geom_raster(binwidth = 1, stat = "summary_2d", fun = mean, na.rm = TRUE) 
```
Here's the same in geom_bin2d at binwidth of 0.25. This provides a count.
```{r}
ggplot(garfield_df, aes(Bedrooms, Baths)) +
  geom_bin2d(binwidth = 0.25, na.rm = TRUE)
```
Here is binwidth = 1
```{r}
ggplot(garfield_df, aes(Bedrooms, Baths)) +
  geom_bin2d(binwidth = 1, na.rm = TRUE)
```

```{r}
ggplot(garfield_df, aes(Bedrooms, Baths, z = Sale_Price)) +
  geom_bin2d(binwidth = 1, na.rm = TRUE, stat = "summary_2d", fun = mean,)
```
Which appears nearly identical to the raster created earlier, very subtle differences in shading possible.
```{r}
ggplot(garfield_df, aes(Bedrooms, Baths, z = Sale_Price)) +
  geom_raster(binwidth = 1, stat = "summary_2d", fun = mean, na.rm = TRUE)
```

```{r}
library(hexbin)
ggplot(garfield_df, aes(Bedrooms, Baths, z = Sale_Price)) +
  geom_hex(binwidth = 1, stat = "summary_2d", fun = mean, na.rm = TRUE)
```

```{r}
ggplot(garfield_df, aes(Bedrooms, Baths, z = Sale_Price)) +
  geom_hex(binwidth = 0.25, stat = "summary_2d", fun = mean, na.rm = TRUE)
```

```{r}
ggplot(garfield_df, aes(Bedrooms, Baths)) +
  geom_hex()
```

#3.11 Displaying Distributions
```{r}
ggplot(garfield_df, aes(Baths)) +
  geom_freqpoly(aes(color = Location), na.rm = TRUE) +
  theme(legend.position = "none")
```

```{r}
ggplot(garfield_df, aes(Baths)) +
  geom_histogram(aes(fill = Location), binwidth = 0.25, position = "fill", na.rm = TRUE) + #Binwidth to match baths increment
  theme(legend.position = "none")
```

```{r}
ggplot(garfield_df, aes(Sale_Price)) +
  geom_histogram(aes(fill = Location), binwidth = 50000, position = "fill", na.rm = TRUE) + #Looked at multiple bin widths
  theme(legend.position = "none")
```

```{r}
ggplot(garfield_df, aes(Sale_Price)) +
  geom_density(na.rm = TRUE) + 
  theme(legend.position = "none")
```

```{r}
ggplot(garfield_df, aes(Sale_Price, fill = Location, color = Location)) +
  geom_density(alpha = 0.2, na.rm = TRUE) + 
  theme(legend.position = "none")
```
We know Carbondale has the expensive listings, so narrowing the xlim
```{r}
ggplot(garfield_df, aes(Sale_Price, fill = Location, color = Location)) +
  geom_density(alpha = 0.2, na.rm = TRUE) +
  xlim(NA, 1500000) + 
  theme(legend.position = "none")
```
And again...
```{r}
ggplot(garfield_df, aes(Sale_Price, fill = Location, color = Location)) +
  geom_density(alpha = 0.2, na.rm = TRUE) +
  xlim(NA, 1000000) + 
  theme(legend.position = "bottom")
```

